Bayesian Detection of Bias in Peremptory Challenges Using Historical Strike Data

### 2023-06-28 analysis/paper_draft4.Rmd
edit to sentence formerly referring to inflated Type I error and reduced power

As a result, for any given estimate of illegal strike bias in a current trial, incompatibility between strike data from that current trial and strike data from past trials can lead to inflated bias detection when no bias exists and reduced power [@Bennett2021]. Other methods to increase power may in turn require adjusting for incompatibility implicitly. For example, @Gastwirth2014 [p. 295-297] stratify strike data by trial and apply the Cochran-Mantel-Haenszel test, albeit after first selecting only historical strike data from past trials that are "similar" in their bias-salient characteristics to the current trial [p. 289, 297]. This initial step presumably aims to reduce incompatibility due to variation in those salient characteristics. Any such choice of "similar" historical strike data would need to be disclosed and justified.

>>>>

As a result, for any given estimate of illegal strike bias in a current trial, incompatibility between strike data from that current trial and strike data from past trials can lead to errors in detecting illegal strike bias (false positives and false negatives) [@Bennett2021]. Other methods to increase power may in turn require adjusting for incompatibility implicitly. For example, @Gastwirth2014 stratify strike data by trial and apply the Cochran-Mantel-Haenszel test [p. 295-297], albeit after first selecting only historical strike data from past trials that are "similar" in their bias-salient characteristics to the current trial [p. 289, 297]. This initial step presumably aims to reduce incompatibility due to variation in those salient characteristics. Any such choice of "similar" historical strike data would need to be disclosed and justified.
